# Prerequisites {-}

This guide is meant to be hands-on and interactive. This means you have the
option of installing the software and playing with it during the workshop using
this guide. But it is still strongly preferred not to spend time getting
everyone setup, so some things are needed in advance.

## R, RStudio and package dependencies {-}

This guide assumes you use R and RStudio as the IDE
([Integrated Development Environment](https://en.wikipedia.org/wiki/Integrated_development_environment)).
Please install them using the link below:

* R: https://www.r-project.org
* RStudio (>= 1.4): https://rstudio.com/products/rstudio/download/#download

All R package dependencies used in this guide can be installed via:

```{r install, eval = FALSE}
install.packages("pak", repos = "https://r-lib.github.io/p/pak/dev")
pak::pkg_install("hongyuanjia/reprod-bes")
```

This guide will teach you how to create a research compendium using R. So basic
knowledge of R programming is preferred. No need to be proficient in R, but you
need to know some R basics, including basic data types, flow controls and
functions.

There are many excellent R programming tutorials on the internet. One of them is
the [beginner materials](https://education.rstudio.com/learn/beginner/) provided
by [RStudio Eduction](https://education.rstudio.com/) center.

For those who never did programming in R before, it is recommended to at least
read through the free online ModernDive chapter
[Getting Started with R and RStudio](https://moderndive.netlify.com/1-getting-started.html).
You may also enjoy the
[Basic Basics](https://rladiessydney.org/courses/ryouwithme/basicbasics)
lesson unit from
[R-Ladies Sydney](https://rladiessydney.org/),
which provides an
[opinionated tour of RStudio](https://rladiessydney.org/courses/ryouwithme/01-basicbasics-1/)
for new users and a step-by-step guide to
[installing and using R packages](https://rladiessydney.org/courses/ryouwithme/01-basicbasics-2/).
You may also try the
[RStudio Primers](https://rstudio.cloud/learn/primers)
interactive R tutorials provided by
[RStudio Cloud](https://rstudio.cloud/).

## Git and GitHub {-}

This guide uses Git for the [version control](https://en.wikipedia.org/wiki/Version_control)
system and [GitHub](https://github.com/) for free hosting Git-based projects.

Please download and install Git via https://git-scm.com/downloads. More detailed
instructions on installing Git can be found in the
[Install Git](https://happygitwithr.com/install-git.html)
chapter in the free online book
[Happy Git and GitHub for the useR](https://happygitwithr.com/)
by
[Jenny Bryan](https://jennybryan.org/).

For those who did not have a GitHub account, follow the instructions in the
[Register a GitHub account](https://happygitwithr.com/github-acct.html)
chapter in the same book above.

## EnergyPlus {-}

This guide uses the U.S. Department of Energy (DOE) medium office reference
building model [@field2010using] distributed together with
[EnergyPlus](https://www.energyplus.net/) for conducting parametric
building energy simulations. EnergyPlus v9.4 should be installed in advanced.
The most straightforward way is using the `install_eplus()` function in the
{eplusr} package. You can install EnergyPlus v9.4 using the code blow:

```{r install-eplus-all, eval = FALSE}
# install EnergyPlus for all users
# NOTE: administrative privileges required
eplusr::install_eplus(9.4)

# OR install EnergyPlus for current user
eplusr::install_eplus(9.4, local = TRUE)
```

By default, it will install EnergyPlus in the default location, which is:

- `C:\EnergyPlusVX-Y-0` on Windows
- `/Applications/EnergyPlus-X-Y-0` on macOS
- `/usr/local/EnergyPlus-X-Y-0` on Linux

where `X-Y-0` is the EnergyPlus version you want to install, e.g. `9-4-0`.

Please note that writing to those locations will require **administrative
privileges** on Windows and **superuser privileges** (`sudo`) on macOS and
Linux.

If you want to install EnergyPlus only for your self, you can do it by
setting `local` to `TRUE` (`FALSE` is the default):

```{r install-eplus-local, eval = FALSE}
# install EnergyPlus for current user
eplusr::install_eplus(9.4, local = TRUE)
eplusr::avail_eplus()
```

The user level EnergyPlus installation path is:

- `%LOCALAPPDATA%\EnergyPlusVX-Y-0` on Windows
- `~/Applications/EnergyPlus-X-Y-0`on macOS
- `~/.local/EnergyPlus-X-Y-0` on Linux

When loaded, the {eplusr} package will search both installation locations of
user level and system level, with the former one taking precedence.

If you have install EnergyPlus v9.4 in a custom location other than the two
above, there is no need to reinstall it. {eplusr} can let you specify that
location using the `use_eplus()` function. Details will be given in [Parametric simulations].

## LaTeX {-}

This guide contains a [chapter][Literate programming] on writing a simple academic
manuscript using [R Markdown](xie2018markdown) with the
[Elsevier LaTeX template](https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions).
LaTeX is needed for compiling PDF from R Markdown. If you don't have LaTeX
installed, considering install `TinyTeX` [@xie2019tinytex], a lightweight (~61Mb
on macOS/Linux and <100Mb on Windows) LaTeX distribution based on TeX Live with
a feature of automatically installing missing packages during compiling.  You
can install `TinyTeX` using the {tinytex} pacakge by running the code below:

```{r tinytex, eval = FALSE}
tinytex::install_tinytex()
```

## Docker {-}

This guide uses [Docker](https://www.docker.com/) [@merkel2014docker] to create
isolated, explict computational environments for building energy simulation.

Docker is a large topic. This guide will only focus on the key concepts and the
minimal steps to create Docker images and run containers.

To install Docker, follow the instructions specific to your operating system:

* [Docker Desktop for Windows](https://docs.docker.com/docker-for-windows/install/)
* [Docker Desktop for macOS](https://docs.docker.com/docker-for-mac/install/)
* [Docker engine for Linux](https://docs.docker.com/engine/install/)

For Windows users, please check if the
[system requirements](https://docs.docker.com/docker-for-windows/install/#system-requirements)
are met, especially the minimal Windows version requirements (Windows 10 64-bit
version 1903 with Build 18362). You can check your current Windows version by
pressing `Win + R`, typing `winver` and pressing `Enter`.
Another requirement of enabling the WSL2
(Windows Subsystem for Linux version 2) can be achieved by opening PowerShell as
Administrator (Press `Win + X` and select `Windows Powershell (Admin)`) and
running the following command.

```powershell
dism.exe /online /enable-feature /featurename:Microsoft-Windows-Subsystem-Linux /all /norestart
```

It is suggested to read through the RStudio
[Docker 101 for Data Scientists](https://environments.rstudio.com/docker.html)
short page to get a rough idea about Doker and its key concepts. You may also
find the official [Docker Get started](https://docs.docker.com/get-started/)
documentation useful.

If you encounter problems when installing Docker, you can still proceed with
this guide to learn how to write the `Dockerfile` for your research compendium.
However, you will not be able to actual build your images and run containers.

